---
title: "initial_model"
output: html_document
date: "2023-06-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(spdep)
library(glmnet)
library(RColorBrewer)
```




## Null simulation data generating

```{r}
set.seed("123")
df <- list()
df$meta <- list()
df$meta$cell <- c(1:500)
df$meta$x <- runif(500, min = 0, max = 100)
df$meta$y <- runif(500, min = 0, max = 100)
df$meta$gene1 <- runif(500, min = 0, max = 1)
df$meta$gene2 <- runif(500, min = 0, max = 1)
df$meta$gene3 <- runif(500, min = 0, max = 1)
df$meta$gene4 <- runif(500, min = 0, max = 1)
df$meta$locat <- data.frame(df$meta$x,df$meta$y)
df$para$dist <- as.matrix(dist(df$meta$locat))

```
*****
##cell type decomposing
```{r}

celltype_dec <- function(obj) {
  obj$meta$cell_type <- max.col(as.matrix(cbind(obj$meta$gene1, obj$meta$gene2, obj$meta$gene3, obj$meta$gene4)))
  return(obj)
}
df <- celltype_dec(df)


```

*****
##plot different cell
```{r}

plot(df$meta$locat, pch=19,cex = 0.5, col = ifelse(df$meta$cell_type %in% c(3,4), "grey", df$meta$cell_type))

table(df$meta$cell_type)
```

*****
## Weighted K-NN for lr pairs

```{r}
get_lr_wknn <- function(obj,sender,receiver, k){
  
  if(!all(c(sender, receiver)) %in% unique(obj$meta$cell_type)) {
    stop("Can not find sender/receiver in the data")}
  else {
    
    distance <- obj$para$dist[obj$meta$cell_type == sender, obj$meta$cell_type == receiver]
    receiver <- list()
    
    receiver$indices <- as.matrix(t(head(apply(distance, 1, function(x)  as.numeric(colnames(distance)[order(x,decreasing = FALSE)])),k)))

    receiver$distances <- t(head(apply(distance, 1, function(x) sort(x, decreasing = FALSE)), k))
    
    weighted_counts <- receiver$distances * matrix( c(1,sqrt(2),sqrt(3)) , nrow = nrow(receiver$distances), ncol = ncol(receiver$distances), byrow = TRUE)
    
    percentile_weight <- head(sort(weighted_counts), length(weighted_counts) * 0.5)
    index_wknn <- t(apply(weighted_counts, 1 , function(x) x %in% percentile_weight))
    
     lr_wknn  <- receiver$indices * index_wknn
     lr_wknn[lr_wknn == 0 ] <- NA
    
    return(lr_wknn)
  }
}
  
  
lr_example <- get_lr_wknn(df,
            sender = 1,
            receiver = 2,
            k = 3)

lr_example
```
  
  
  ***
## test
```{r}

AA =  df$para$dist[df$meta$cell_type == 1, df$meta$cell_type == 2]
AB <- as.matrix(t(head(apply(AA, 1, function(x)  as.numeric(colnames(AA)[order(x,decreasing = FALSE)])),3)))


AC <- t(head(apply(AA, 1, function(x) sort(x,decreasing = FALSE)),3))


WC <- AC* matrix(1:3, nrow = nrow(AC), ncol = ncol(AC), byrow = TRUE)
hist(sort(WC),50)
length(WC[WC<30])/length(WC)
PP <- head(sort(WC), length(WC) * 0.5)
IND <- t(apply(WC, 1 , function(x) x %in% PP))
AB <- AB*IND

# AB = lr_example
AB[AB == 0 ] <- NA



CI <- unique(as.numeric(c(rownames(AB),as.numeric(AB))))
# cell_index <- unique(c(as.numeric(rownames(lr_pair),as.numeric(lr_pair))))


CM <-df$meta$locat[CI,]
# cell_meta <- df$meta$locat[cell_index, ]


LI <- create_lr_index(AB)
ABX <-  rep(row.names(AB), each = ncol(AB))
ABY <-  as.vector(t(AB))
ABM <- cbind(ABX,ABY)

plot(df$meta$locat, pch=19,cex = 0.5, col = ifelse(df$meta$cell_type %in% c(3,4), "grey", df$meta$cell_type))
text(df$meta$x[CI],df$meta$y[CI], CI, pos = 3)
 
 
CM <- df$meta$locat[unique(LI),]
 length(CI)
  CM
  
  
  plot(df$meta$locat, pch=19,cex = 0.5, col = ifelse(df$meta$cell_type %in% c(3,4), "grey", df$meta$cell_type))
i = 1
      A = LI[i,1]
      B = LI[i,2] 
      x1 <- CM[rownames(CM) == A, 1]
      y1 <- CM[rownames(CM) == A, 2]
      x2 <- CM[rownames(CM) == B, 1]
      y2 <- CM[rownames(CM) == B, 2]
      arrows(x1, y1, x2, y2, length = 0.1)

NCR <- AB[AB[,1] == 5,]



```



## create lr index **
```{r}
 create_lr_index <- function(lrpair){
    A = rep(row.names(lrpair), each = ncol(lrpair))
    B = as.vector(t(lrpair))
    lr_index <- cbind(A,B)
    
    lr_index <- lr_index[complete.cases(lr_index),]
    return(lr_index)
  }


lr_index_example <- create_lr_index(lr_example)

```

****
##  plot lr pairs **
```{r}
find_row_list_number <- function(lr_index,list_of_lists) {
       for (i in 1: length(list_of_lists)) {
          if (all(lr_index %in% list_of_lists[[i]])) {
                       ind = i 
                        break
          }
       }
  return(ind)
}

plot_lr_pair <- function(obj, lr_pair, arrows = T, cluster = list()){
  
   cell_index <- unique(as.numeric(c(rownames(lr_pair),as.numeric(lr_pair))))
  
    lr_index <- create_lr_index(lr_pair)
    
    cell_meta <- obj$meta$locat[unique(lr_index),]
 
  plot(df$meta$locat, pch=19,cex = 0.5, col = ifelse(obj$meta$cell_type %in% c(3,4), "grey", df$meta$cell_type))
  
  text(df$meta$x[cell_index],df$meta$y[cell_index], cell_index, pos = 3)
  

for (i in 1:nrow(lr_index)) {
      A = lr_index[i,1]
      B = lr_index[i,2]
      x1 <- cell_meta[rownames(cell_meta) == A, 1]
      y1 <- cell_meta[rownames(cell_meta) == A, 2]
      x2 <- cell_meta[rownames(cell_meta) == B, 1]
      y2 <- cell_meta[rownames(cell_meta) == B, 2]
      
      
if (length(cluster) == 0 ){
if (arrows)  {
   arrows(x1, y1, x2, y2, length = 0.1)
}
else{
    lines(c(x1, x2), c(y1, y2), col = 1 )
}
      
}
  else{
    
    if (arrows)  {
   arrows(x1, y1, x2, y2, length = 0.1, col =as.numeric(find_row_list_number(cluster, lr_index[i, ])))
     }
else{
      lines(c(x1, x2), c(y1, y2), col = as.numeric(find_row_list_number(cluster, lr_index[i, ])))
     }
  }
  
}
}


#example  


    plot_lr_pair(df, lr_example,)

    
    
```


##create network **

###provided by chatgpt version
```{r}
create_lr_index <- function(lrpair) {
  A <- rep(row.names(lrpair), each = ncol(lrpair))
  B <- as.vector(t(lrpair))
  lr_index <- cbind(A, B)
  
  lr_index <- lr_index[complete.cases(lr_index), ]
  return(lr_index)
}

create_lr_network <- function(obj, lr_pair) {
  lr_index <- create_lr_index(lr_pair)
  
  connected_dots <- list()
  
  for (i in 1:ncol(lr_index)) {
    edges <- as.vector(t(lr_index[, i, drop = FALSE]))
    edges <- na.omit(edges)
    
    if (length(edges) > 1) {
      connected_dots[[i]] <- edges
    }
  }
  
  return(connected_dots)
}

# Example usage
network <- create_lr_network(df, lr_example)
    
network

lr_index_example





[[1]]
"6"   "342"


[[2]]

"8"   "38" 
"141" "38" 
"212" "38" 
"141" "38" 



```

### creat_network
```{r}
create_lr_network <- function(obj, lr_pair, plot = TRUE) {
  
   cell_index <- unique(c(as.numeric(rownames(lr_pair),as.numeric(lr_pair))))
   
    lr_index <- create_lr_index(lr_pair)
    
    cell_meta <- obj$meta$locat[unique(lr_index),]
    
    
  # plots
    
  if (plot) {
    plot_lr_pair(obj, lr_pair, arrows = F)
   }
    

   # Creat network
    networks <- list() 
    
    j  = 1
    
 
   # Create network process
  while (nrow(lr_index) > 0) {
    
       connected_rows <- t(as.matrix(lr_index[1,]))
       ligand <- connected_rows[1,1]
       receptor <- connected_rows[1,2]
       

       
       #update_lr_index
       lr_index <- lr_index[!(lr_index[, 1]== ligand & lr_index[, 2] == receptor), ]
       possible_connect <- lr_index[lr_index[, 1]== ligand | lr_index[, 2] == receptor, ]
       
      connected_rows <- as.matrix(rbind(connected_rows, possible_connect))
      
        # update  lr_index
       
       
       # find edges
    if(length(possible_connect) == 0){
      networks[[j]] = connected_rows
      j = j+1
      
      lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
   
      print(networks)
      
       }
    
       
    # length(possible_connect) > 0
    else {
      #possible_connect
   
       lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows), ]
    
     new_rows_group <-  lr_index[(lr_index[, 1] %in% connected_rows[, 1] | lr_index[, 2] %in% connected_rows[, 2] ), ]
     
      while( length(new_rows_group) > 0  ){
        #merge
        connected_rows <- rbind(connected_rows, new_rows_group)
        # update  lr_index
       lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[,2]), ]
   
    
     new_rows_group ->  lr_index[lr_index[, 1] %in% connected_rows[, 1] | lr_index[, 2] %in% connected_rows[, 2], ]
      
     ## if loop for new rows
       
      while( nrow(new_rows_group)>0) {
      
      for (i in 1: nrow(new_rows_group)){
      
        ligand <- new_rows_group[i, 1]
        receptor <- new_rows_group[i, 2]
        
       new_rows <- lr_index[lr_index[, 1]== ligand | lr_index[, 2] == receptor, ]
        
       new_rows_group <- rbind(new_rows_group, new_rows)
      
       
      }
      
       lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows), ]
    
     new_rows_group ->  lr_index[(lr_index[, 1] %in% connected_rows[, 1] | lr_index[, 2] %in% connected_rows[, 2] ), ]
     
    }
     
     connected_rows <- rbind(connected_rows, new_rows_group)
      
      networks[[j]] = connected_rows
       j = j + 1
      
    }
  }
      
}
return(networks)
    
}

# Example usage
network_example <- create_lr_network(df, lr_example)







single_network <- function( connected_rows,lr_index, new_rows_group){
  # length(possible_connect) > 0
      #merge
    connected_rows <- rbind(connected_rows, new_rows_group)
        # update  lr_index
     lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[,2] %in% connected_rows), ]
    
     new_rows_group ->  lr_index[(lr_index[, 1] %in% connected_rows[, 1]|lr_index[,2] %in% connected_rows[, 2]), ]
     
    while( nrow(new_rows_group)>0) {
      
      for (i in 1: nrow(new_rows_group)){
      
        ligand <- new_rows_group[i, 1]
        receptor <- new_rows_group[i, 2]
        
       new_rows <- lr_index[lr_index[, 1]== ligand | lr_index[, 2] == receptor, ]
        
       new_rows_group <- rbind(new_rows_group, new_rows)
      
       
      }
      
       lr_index <- lr_index[!(lr_index[, 1] %in% connected_row[, 1] & lr_index[, 2] %in% connected_row), ]
    
     new_rows_group ->  lr_index[(lr_index[, 1] %in% connected_row[, 1] | lr_index[, 2] %in% connected_ro[, 2] ), ]
     
    }
     
     connected_row <- rbind(connected_row, new_rows_group)
     
     
      return(connect_row, lr_index)
      
      
      
    }
    
    
    
  
single_network(lr_index_example[2,],lr_index_example )






 lr_index2 <- lr_index_example[!lr_index_example[, 1] %in% lr_index_example[1, 1] & !lr_index_example[, 2] %in% lr_index_example[1, 1], , drop = FALSE]
 
 
 example_length<- lr_index2[lr_index2[, 2] %in% lr_index_example[2, 2], , drop = FALSE]

 PC <- lr_index_example[lr_index_example[, 1]== 8| lr_index_example[, 2] == 38, ]

 dim(lr_index_example)
 lr_index2 <- lr_index_example[!(lr_index_example[, 1] %in% PC[, 1] & lr_index_example[, 2] %in% PC[, 2]), ]
 dim(lr_index2)

 PC
 

 
 
 dim(lr_index2)
 
 
 lr_index_example[!lr_index_example[, 1] %in% lr_index2[, 1] & !lr_index_example[, 2] %in% lr_index2[, 1], , drop = FALSE]
 
 dim(lr_index_example)
 
example_length



```



## example
```{r}
create_lr_network <- function(obj, lr_pair, plot = TRUE) {
  cell_index <- unique(c(as.numeric(lr_pair[, 1]), as.numeric(lr_pair[, 2])))
  lr_index <- create_lr_index(lr_pair)
  cell_meta <- obj$meta$locat[unique(lr_index), ]
  
  if (plot) {
    plot_lr_pair(obj, lr_pair, arrows = FALSE)
  }
  
  networks <- list()
  j <- 1
  
  while (nrow(lr_index) > 0) {
    
    connected_rows <- as.matrix(lr_index[1, ])
    ligand <- connected_rows[1, 1]
    receptor <- connected_rows[1, 2]
    
    lr_index <- lr_index[lr_index[, 1] != ligand & lr_index[, 2] != receptor, ]
    possible_connect <- lr_index[lr_index[, 1] == ligand | lr_index[, 2] == receptor, ]
    
    while (nrow(possible_connect) > 0 ) {
      
      connected_rows 
      
      
    }
    
    
    
    
    
    if (nrow(possible_connect) == 0) {
      networks[[j]] <- connected_rows
      j <- j + 1
    } else {
      
      
      new_rows_group <- possible_connect
      
      while (nrow(new_rows_group) > 0) {
        connected_rows <- rbind(connected_rows, new_rows_group)
        lr_index <- lr_index[!(lr_index[, 1] %in% new_rows_group[, 1] & lr_index[, 2] %in% new_rows_group[, 2]), ]
        new_group <- matrix()
        
        for (i in 1:nrow(new_rows_group)) {
          ligand <- new_rows_group[i, 1]
          receptor <- new_rows_group[i, 2]
          
          new_rows <- lr_index[lr_index[, 1] == ligand | lr_index[, 2] == receptor, ]
          
          lr_index <- lr_index[!(lr_index[, 1] %in% new_rows[, 1] & lr_index[, 2] %in% new_rows[, 2]), ]
          
          new_group <- rbind(new_group, new_rows)
        }
        
        new_rows_group <- new_group
        connected_rows <- rbind(connected_rows, new_rows_group)
      }
      
      lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
      
      networks[[j]] <- as.matrix(connected_rows)
      j <- j + 1
      
    }
    
      
  }
  
  return(networks)
}

# Example usage
network_example <- create_lr_network(df, lr_example)
network_example
```






## example2 (currently working on)


```{r}
create_lr_network <- function(obj, lr_pair, plot = TRUE) {
 
  lr_index <- create_lr_index(lr_pair)
  
  
  lr_index <- as.matrix(lr_index)
  
  if (plot) {
    plot_lr_pair(obj, lr_pair, arrows = FALSE)
  }
  
  networks <- list()
  j <- 1
  
  while (nrow(lr_index) > 0) {
    ## connected_rows <- lr_index[1, ])

    connected_rows <- lr_index[1, ]
    
    
    lr_index <- lr_index[!(lr_index[, 1] == lr_index[1,1] & lr_index[, 2] == lr_index[1,2]), ]
    print ( class(connected_rows))
    
    possible_connect <- lr_index[lr_index[, 1] == connected_rows[1,1] | lr_index[, 2] == connected_rows[1,2], ]
    

    if (!isTRUE(possible_connect) || !nrow(new_rows_group) > 0) {
      networks[[j]] <- connected_rows
      j <- j + 1
      possible_connect <- lr_index[lr_index[, 1] == connected_rows[,1] | lr_index[, 2] == connected_rows[,2], ]
       connected_rows <- matrix()
    }
    
    else {
      
      connected_rows <- rbind(connected_rows, possible_connect)
      new_rows_group  <-  possible_connect


      while ( isTRUE(new_rows_group) && nrow(new_rows_group) > 0) {
        connected_rows <- rbind(connected_rows, new_rows_group)
        
        lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
        
        new_rows_group <- lr_index[lr_index[, 1] %in% connected_rows[, 1]| lr_index[, 2] %in% connected_rows[, 2], ]
        
         connected_rows <- rbind(connected_rows, new_rows_group)
         
          for (i in 1:nrow(new_rows_group)) {
            ligand <- new_rows_group[i, 1]
            receptor <- new_rows_group[i, 2]
            
            new_rows <- lr_index[lr_index[, 1] == ligand | lr_index[, 2] == receptor, ]
            
            new_rows_group <- rbind(new_rows_group, new_rows)
          }
          
          lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
          
          new_rows_group <- lr_index[lr_index[, 1] %in% connected_rows[, 1] | lr_index[, 2] %in% connected_rows[, 2], ]
          connected_rows <- rbind(connected_rows, new_rows_group)
          
      }
      
       connected_rows <- rbind(connected_rows, new_rows_group)
        lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
       
    }
    
      
      networks[[j]] <- connected_rows
      j <- j + 1
      
      lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
       connected_rows <- matrix()
      
       }
  return(networks)

  }
  
  



# Example usage
network_example <- create_lr_network(df, lr_example)
network_example


```

## example
Here's the modified code:(currently work on )

```{r}
create_lr_network <- function(obj, lr_pair, plot = TRUE) {
  lr_index <- create_lr_index(lr_pair)
  lr_index <- as.matrix(lr_index)
  
  if (plot) {
    plot_lr_pair(obj, lr_pair, arrows = FALSE)
  }
  
  networks <- list()
  j <- 1
  
  while (nrow(lr_index) > 0) {
    connected_rows <- lr_index[1, , drop = FALSE]
    
    lr_index <- lr_index[!(lr_index[, 1] == connected_rows[1, 1] & lr_index[, 2] == connected_rows[1, 2]), ]
    
    possible_connect <- lr_index[lr_index[, 1] == connected_rows[1, 1] | lr_index[, 2] == connected_rows[1, 2], ]
    
    print("Connected Rows:")
    print(connected_rows)
    print("Possible Connect:")
    print(possible_connect)
    
    if (is.null(possible_connect) || nrow(possible_connect) == 0) {
      networks[[j]] <- connected_rows
      j <- j + 1
      connected_rows <- matrix()
    } else {
      connected_rows <- rbind(connected_rows, possible_connect)
      
      while (nrow(possible_connect) > 0) {
        lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
        
        new_rows_group <- lr_index[lr_index[, 1] %in% connected_rows[, 1] | lr_index[, 2] %in% connected_rows[, 2], ]
        
        possible_connect <- setdiff(new_rows_group, connected_rows)
        
        print("New Rows Group:")
        print(new_rows_group)
        print("Updated Possible Connect:")
        print(possible_connect)
        
        connected_rows <- rbind(connected_rows, possible_connect)
      }
      
      networks[[j]] <- connected_rows
      j <- j + 1
      
      # Update lr_index with remaining rows
      lr_index <- lr_index[!(lr_index[, 1] %in% connected_rows[, 1] & lr_index[, 2] %in% connected_rows[, 2]), ]
    }
  }
  
  return(networks)
}








network_example <- create_lr_network(df, lr_example)

```

## model for points *****
```{r}

find_next_connected_point <- function(this_point, point_column_index, lr_index) {
  opposite_column_index = 3 - point_column_index
  cluster_points = list(this_point)
  if (is.null(dim(lr_index))) return (unique(cluster_points))
  connected_points <- lr_index[lr_index[, point_column_index] == this_point, opposite_column_index]
  if (length(connected_points)>0) {
    for (connect_point in connected_points){
      if (is.null(dim(lr_index))) break
      lr_index = lr_index[! ( (lr_index[, point_column_index] == this_point) & (lr_index[, opposite_column_index] == connect_point) ), ]
      next_points = find_next_connected_point(connect_point, opposite_column_index, lr_index)
      cluster_points = rbind(cluster_points, next_points)
    }
  } 
  return (unique(cluster_points))
}

delete_points_from_df <- function(points, lr_index) {
  for (point in points){
     if (is.null(dim(lr_index))) break
     lr_index <- lr_index[(lr_index[, 1] != point) & (lr_index[, 2] != point), ]
  }
  return (lr_index)
}



find_point <- function (lr_index) {
  
  lr_index = rbind(lr_index, c(-1,-1))
  network = list()
  network_index= 1

  while (!is.null(dim((lr_index)))){
   current_point = lr_index[1,1]
   cluster_points = unique(find_next_connected_point(current_point, 1, lr_index))
   network[[network_index]] = cluster_points
   network_index = network_index + 1
   lr_index = delete_points_from_df(cluster_points, lr_index)
}
  return(network)
}


create_lr_network <- function(obj, lr_pair, plot = TRUE) {
  
  
  lr_index <- create_lr_index(lr_pair)
  
  #To be con
  point_within <- find_point(lr_index)
  network = list()
  
  for( i in 1:length(point_within) ){
    network[[i]] <- lr_index[lr_index[,1] %in% point_within[[i]] & lr_index[,2] %in% point_within[[i]],]
    
  }
  
   if (plot == TRUE) {
    plot_lr_pair(df, lr_example, arrows = F, cluster = network )
  }
  
  
  return(network)
  
}
  
aab <- create_lr_network(df, lr_example, plot = TRUE)

```




```{r}

edges <- matrix(c(1, 2,
                  2, 3,
                  3, 4,
                  4, 1), ncol = 2, byrow = TRUE)

# Function to find all connected lines
find_lines <- function(edges) {
  lines <- list()  # List to store the lines
  
  while (nrow(edges) > 0) {
    line <- vector()  # Vector to store the current line
    
    # Find the first point of the line
    start_point <- edges[1, 1]
    
    # Loop until the line is closed or there are no more connected points
    while (TRUE) {
      # Find the next connected point
      next_point <- edges[edges[, 1] == start_point, 2]
      
      if (length(next_point) == 0) {
        break  # No more connected points, close the line
      }
      
      # Add the current point to the line
      line <- c(line, start_point)
      
      # Remove the edge from the matrix
      edges <- edges[-which(edges[, 1] == start_point), ]
      
      # Set the next point as the start point for the next iteration
      start_point <- next_point
    }
    
    # Add the line to the list
    lines[[length(lines) + 1]] <- c(line, start_point)  # Close the line
  }
  
  return(lines)
}

# Find all connected lines
lines <- find_lines(edges)

# Print the lines
for (i in seq_along(lines)) {
  cat("Line", i, ":", paste(lines[[i]], collapse = " -> "), "\n")
}




```



## spatial autoregressive model
```{r}
index_unique <- unique(as.numeric(lr_index_example))
 list_nb = list()
for (i in ncol(index_unique)){
row_a <- lr_index_example[lr_index_example[1,] & lr_index_example[,2] %in%  index_unique[i], ]
  row_a <- unique(as.numeric(row_a))
  row_a <- setdiff(row_a, index_unique[i])
  nb[[i]] <- row_a
}

nb = nb(list_nb)
 W <- nb2listw(nb)
data <- data.frame(
reccptor = df$meta$gene2[index_unique,],
ligand = df$meta$gene1[index_unique, ],
neighbor_list = W
)


model <- lagsarlm(reccptor ~ ligand, data = data, listw = W)

summary(model)

```


## SVC model * dataset create ***
```{r}
build_dataset <- function(df, lr) {
  lr_network <- create_lr_network(df, lr, plot = FALSE)
  dataset <- vector("list", length(lr_network))  
  
  # Initialize dataset as a list with the required number of elements

  for (j in 1:length(lr_network)) {
    single_network <- lr_network[[j]]

    for (i in 1:(length(single_network)/2)) {
      
      if (length(single_network)/2 < 2) {
        ligand <- as.numeric(single_network[[1]])
        receptor <- as.numeric(single_network[[2]])
      } else {
        row <- single_network[i, ]
        ligand <- as.numeric(row[1])
        receptor <- as.numeric(row[2])
      }
      
      gene_class_L <- df$meta$cell_type[ligand]
      gene_class_R <- df$meta$cell_type[receptor]
      
      expression <- cbind(df$meta$gene1, df$meta$gene2, df$meta$gene3, df$meta$gene4)
      x <- expression[ligand, gene_class_L]
      y <- expression[receptor, gene_class_R]
      
      new_expression_row <- c(x, y)
      dataset[[j]] <- rbind(dataset[[j]], new_expression_row)
    }
  }
  
  return(dataset)
}

df_example <- build_dataset(df, lr_example)






```




## actual model
```{r}
# Load the required package


# Define the function
fit_sparse_cluster <- function(X, Y, lambda1, lambda2, clusters) {
  n_clusters <- length(clusters)
  betas <- vector("list", n_clusters)
  
  for (i in 1:n_clusters) {
    cluster_data <- X[[i]]
    Y_cluster <- Y[[i]]
    
    # Fit Lasso regularization using glmnet
    fit <- glmnet(cluster_data, Y_cluster, alpha = 0, lambda = lambda1, standardize = FALSE)
    
    # Calculate R2 within the cluster
    X_spatial <- abs(diff(cluster_data, differences = 1))
    R2 <- lambda2 * abs(X_spatial %*% as.matrix(fit$beta))
    
    # Total loss function
    loss <- sum((Y_cluster - cluster_data %*% as.matrix(fit$beta))^2) / (2 * length(Y_cluster))
    total_loss <- loss + sum(R2)
    
    # Store the betas for the cluster
    betas[[i]] <- as.matrix(fit$beta)
  }
  
  return(betas)
}

# Define lambda values
lambda1 <- 0.1
lambda2 <- 0.05

# Apply the model on the dataset
result <- fit_sparse_cluster(df_example, df_example, lambda1, lambda2, seq_along(df_example))

# Show the results
for (i in seq_along(result)) {
  cat("Cluster", i, ":\n")
  print(result[[i]])
  cat("\n")
}





```






## actual model2 ******
```{r}

optimize_model1 <- function(df, lambda1, lambda2) {
  n <- nrow(df)
  k <- ncol(df) / 2
  
  X <- matrix(df[, 2], nrow = n, ncol = 1)
  Y <- df[, 1]
  

  penalty_R1 <- function(beta) {
    sum(beta)
  }
  

  penalty_R2 <- function(beta) {
    sum(abs(diff(beta)))
  }
  
  objective <- function(beta, X, Y, lambda1, lambda2) {
    n <- length(Y)
    L <- 0.5 * sum((Y - X %*% beta)^2) / n
    R1 <- lambda1 * penalty_R1(beta)
    R2 <- lambda2 * penalty_R2(beta)
    L + R1 + R2
  }
  

  initial_beta <- rep(0,1)
  result <- optim(
    initial_beta,
    objective,
    X = X,
    Y = Y,
    lambda1 = lambda1,
    lambda2 = lambda2,
    method = "L-BFGS-B"
  )
  return(result)
}

lambda1 <- 0.1
lambda2 <- 0.2

optimize_model2 <- function(df, lambda1, lambda2) {
  # Initialize an empty list to store the beta coefficients for each row
  beta_list <- list()
  
  # Iterate over each row in the dataset
  for (i in 1:nrow(df)) {
    # Create the design matrix X and response variable Y for the current row
    X <- matrix(df[i, ], nrow = 1, ncol = ncol(df), byrow = TRUE)
    Y <- matrix(df[i, ], nrow = 1, ncol = 1)
    
    # Define the objective function
    objective_function <- function(beta) {
      # Calculate the residuals
      residuals <- Y - X %*% beta
      
      # Calculate the squared sum of residuals
      L <- sum(residuals^2) / (2 * nrow(X))
      
      # Calculate the penalty terms
      R1 <- lambda1 * sum(abs(beta))
      R2 <- lambda2 * sum(abs(diff(beta)))
      
      # Calculate the overall objective value
      objective_value <- L + R1 + R2
      
      return(objective_value)
    }
    
    # Perform the optimization
    result <- optim(par = rep(0, ncol(X)), fn = objective_function, method = "L-BFGS-B", lower = 0)
    
    # Store the beta coefficients for the current row
    beta_list[[i]] <- result$par[[2]]
  }
  
  return(beta_list)
}

lambda1 <- 0.1
lambda2 <- 0.1

beta_coefficients <- optimize_model2(df_example[[1]], lambda1, lambda2)



beta_a <- list()
for(i in 1:length(df_example)){
    beta_all<- as.matrix(optimize_model2(df_example[[i]],lambda1, lambda2))
    beta_a[[i]] <- beta_all
}


beta_a

```




##plot lr connection

```{r}
##  plot lr pairs **
find_row_list_number <- function(lr_index,list_of_lists) {
         
  
       for (i in 1: length(list_of_lists)) {
          if (all(lr_index %in% list_of_lists[[i]])) {
                       ind = i 
                        break
          }
       }
  return(ind)
}

plot_lr_pair <- function(obj, lr_pair, arrows = T, cluster = list(), beta_list){
  
  
  # Define the color gradient
  
  n_colors <- 100
color_palette <- colorRampPalette(brewer.pal(9, "Blues"))(n_colors)

color_index <- unlist(beta_list)
min_col <- min(color_index)
max_col <- max(color_index)
color_index <- ceiling((color_index - min_col) / (max_col - min_col) * n_colors)


# Get RGB values from the color palette
color_rgb <- col2rgb(color_palette)

# Define a function to calculate line color based on the color index
get_line_color <- function(color_index) {
  alpha <- 0.3  # Adjust the transparency as desired
  rgb(color_rgb[1, color_index], color_rgb[2, color_index], color_rgb[3, color_index], maxColorValue = 255, alpha = alpha)
}

  

###
   cell_index <- unique(as.numeric(c(rownames(lr_pair),as.numeric(lr_pair))))
  
    lr_index <- create_lr_index(lr_pair)
    
    cell_meta <- obj$meta$locat[unique(lr_index),]
 
  plot(df$meta$locat, pch=19,cex = 0.5, col = ifelse(obj$meta$cell_type %in% c(3,4), "grey", df$meta$cell_type))
  
  text(df$meta$x[cell_index],df$meta$y[cell_index], cell_index, pos = 3)
  

for (i in 1:nrow(lr_index)) {
      A = lr_index[i,1]
      B = lr_index[i,2]
      x1 <- cell_meta[rownames(cell_meta) == A, 1]
      y1 <- cell_meta[rownames(cell_meta) == A, 2]
      x2 <- cell_meta[rownames(cell_meta) == B, 1]
      y2 <- cell_meta[rownames(cell_meta) == B, 2]
      col_index <- get_line_color(color_index[i])
        
      
if (length(cluster) == 0 ){
if (arrows)  {
   arrows(x1, y1, x2, y2, length = 0.1, col = col_index)
}
else{
   lines(c(x1, x2), c(y1, y2), col = col_index)
  
}
      
}
  else{
    
    if (arrows)  {
   arrows(x1, y1, x2, y2, length = 0.1, col = col_index)
     }
else{
      lines(c(x1, x2), c(y1, y2), col = col_index)
  
     }
  }
  
}
}


#example  


    plot_lr_pair(df, lr_example, arrows = F, beta_list = beta_a)

    
    
```



```


